Species persistence under climate and fishing

### 2014-02-11 Writing/plots/figureCode/MPA_figs.Rmd
Updated consMPA simulations

# Comparing MPAs to each other, to no management

@@

# for synced online github data
  x = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/noMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL25vTVBBbm90VGhyZXNoX2FkZF8yMDEzLTEyLTA5LmNzdiIsImV4cGlyZXMiOjEzOTEyNjg5OTB9--e041d4ef68764b1fc49140c128bda685c6f740f3")
  sim = read.csv(textConnection(x))

  fish = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/fishMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2Zpc2hNUEFub3RUaHJlc2hfYWRkXzIwMTMtMTItMDkuY3N2IiwiZXhwaXJlcyI6MTM5MTI2OTAzM30%3D--f35f2593a7e901c900188fadca920fdd68a57e35")
  fishmpa = read.csv(textConnection(fish))

  cons = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/consMPAnotThresh_add_2014-01-23.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2NvbnNNUEFub3RUaHJlc2hfYWRkXzIwMTQtMDEtMjMuY3N2IiwiZXhwaXJlcyI6MTM5MTI2OTA3Mn0%3D--ffb8451d33daaeab48f8b3be3357cacbda0aadbb")
  consmpa = read.csv(textConnection(cons))
```

@@

  par(oma=oma)
  image.plot(cvals,hvals,ebm,breaks=cuts,col=mycols,
    xlab="Rate of environmental shift",ylab="Harvesting rate",
  	cex.lab=cex.lab,cex.axis=cex.axis, 
  	yaxs=yaxs,xaxs=xaxs,axes=TRUE,
  	legend.shrink=1,legend.width=.1,zlim=range(cuts),
  	axis.args=list(at=myaxes$z$at,labels=myaxes$z$labels,cex.axis=cex.axis),
  	legend.args=list(text="Equilibrium biomass",cex=cex.lab,side=2,line=0.5,las=0),
  	bigplot=c(.13,.85,.15,.95),smallplot=c(.91,.95,.15,.95),horizontal=FALSE)
  box()
}
```

>>>>

# Comparing MPAs to each other, to no management using figure plot code

@@

# for synced online github data
x = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/noMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL25vTVBBbm90VGhyZXNoX2FkZF8yMDEzLTEyLTA5LmNzdiIsImV4cGlyZXMiOjEzOTI2NDYxMDl9--46e45a3eb2faef7fc22b6124253c925bd2290de9")
sim = read.csv(textConnection(x))

fish = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/fishMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2Zpc2hNUEFub3RUaHJlc2hfYWRkXzIwMTMtMTItMDkuY3N2IiwiZXhwaXJlcyI6MTM5MjY0NjE0NH0%3D--8eff4ee16d08efcf6b266c3e4e42adde7aeff969")
fishmpa = read.csv(textConnection(fish))

cons = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/consMPAnotThresh_add_2014-01-23.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2NvbnNNUEFub3RUaHJlc2hfYWRkXzIwMTQtMDEtMjMuY3N2IiwiZXhwaXJlcyI6MTM5MjY0NjE2Nn0%3D--586d3cb31ac0f1fe3c49f48886e3796b5132bb77")
consmpa = read.csv(textConnection(cons))
```

@@

  par(oma=oma)
  image.plot(cvals,hvals,ebm,breaks=cuts,col=mycols,
             xlab="Rate of environmental shift",ylab="Harvesting rate",
             cex.lab=cex.lab,cex.axis=cex.axis, 
             yaxs=yaxs,xaxs=xaxs,axes=TRUE,
             legend.shrink=1,legend.width=.1,zlim=range(cuts),
             axis.args=list(at=myaxes$z$at,labels=myaxes$z$labels,cex.axis=cex.axis),
             legend.args=list(text="Equilibrium biomass",cex=cex.lab,side=2,line=0.5,las=0),
             bigplot=c(.13,.85,.15,.95),smallplot=c(.91,.95,.15,.95),horizontal=FALSE)
  box()
}
```
Results of all simulations

```{r results}
par(mfrow=c(1,3))
noMang <- plotfig(sim); plotParams(noMang)
fish <- plotfig(fishmpa); plotParams(fish)
cons <- plotfig(consmpa); plotParams(cons)
```
